---
title: "Instructions"
output: pdf_document
params:
  json_path: NULL
  labware_images_dir: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(rjson)
library(knitr)
json_data <- fromJSON(file = params$json_path)
```
\vspace{-1.5cm}
## Protocol 1: Heat-Shock Transformation in OT-2

### Overview
DNA is transferred to competent cells.
Pre heat-shock, the cells and added DNA are incubated at `r json_data$pre_shock_incubation_temp` 째C for `r json_data$pre_shock_incubation_time` minutes.
Heat-shock is carried out at `r json_data$heat_shock_temp` 째C for `r json_data$heat_shock_time` seconds.
Post heat-shock, the transformed cells are incubated at `r json_data$post_shock_incubation_temp` 째C for `r json_data$post_shock_incubation_time` minutes.
The recovery medium is added and cells are incubated at `r json_data$recovery_temp`째C for `r json_data$recovery_time` minutes.

### Preparation
Prepare the reagents and labware according to the below diagrams.
Volumes (uL) indicate how much of reagents will be used, so add additional volume.

```{r import-labware-images, results='asis', echo=FALSE}
# Read all image files from the directory
image_files <- list.files(path = params$labware_images_dir, pattern = "\\.png$", full.names = TRUE)
# Sort files numerically and alphabetically
image_files <- sort(image_files)

# Print images in Markdown format, 2 per row
for (i in seq_along(image_files)) {
  # Start a new line for every pair of images
  if (i %% 2 == 1 && i > 1) {
    cat('\\newline\n')
  }
  
  cat(sprintf('![](%s){width=49%%}', image_files[i]))

  if (i %% 2 != 0 && i < length(image_files)) {
    cat(' ')
  }
}
```

### Deck Loading
Check that `r json_data$right_pipette_name` is in the right mount and `r json_data$left_pipette_name` is in the left mount.
**Slot `r json_data$right_pipette_tiprack_slot`** load `r json_data$right_pipette_tiprack_name` for the `r json_data$right_pipette_name` pipette.
**Slot `r json_data$left_pipette_tiprack_slot`** load `r json_data$left_pipette_tiprack_name` for the `r json_data$left_pipette_name` pipette.
**Slot `r json_data$dna_plate_slot`** load `r json_data$dna_plate_name` containing DNA.
**Slot `r json_data$cells_plate_slot`** load `r json_data$cells_plate_name` containing competent cells.
**Slot `r json_data$media_plate_slot`** load `r json_data$media_plate_name` containing recovery medium.
**Slot 7,8,10,11** load a thermocycler and turn it on. Load `r json_data$transformation_plate_name` into the thermocycler when instructed on the screen.