---
title: ""
output: pdf_document
params:
  json_path: NULL
  labware_images_dir: NULL
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(rjson)
library(knitr)
json_data <- fromJSON(file = params$json_path)
```

# APEX Instructions
## Protocol 2: Colony Selection in OT-2

### Deck Loading
1. Load pipettes:
   - **Mount `r json_data$pipette_mount`**: Confirm `r json_data$pipette_name` is properly installed

2. Load tip racks:
   - **Slot `r json_data$tiprack_slots`**: Place `r json_data$tiprack_name` for use with `r json_data$pipette_name` pipette

3. Load plates:
   - **`Thermocycler`**: Place `r json_data$transformation_plate_name` containing cells to be spotted
   - **Slot `r json_data$agar_plate_slot`**: Place `r json_data$agar_plate_name` with LB agar

### Preparation
Prepare reagents and labware according to the plate layout shown below. All volumes are in `r "$\\mu$L"`. Include additional volume for accurate pipetting.

```{r source-plate-images, results='asis', echo=FALSE}
image_files <- list.files(path = params$labware_images_dir, pattern = "\\.png$", full.names = TRUE)
image_files <- sort(image_files)
if(length(image_files) > 1) {
  for (i in 1:(length(image_files)-1)) {
    if (i %% 2 == 1 && i > 1) {
      cat('\n\n')
    }
    cat(sprintf('![](%s){width=49\\%%}', image_files[i]))
    if (i %% 2 != 0 && i < (length(image_files)-1)) {
      cat(' ')
    }
  }
} else {
  cat("*No plate layout images available*")
}
```

### Protocol Execution
1. **Cell Aspiration**: APEX aspirates transformed cells with an additional `r json_data$additional_volume` `r "$\\mu$L"` volume to ensure accurate spotting.

2. **Agar Height Calculation**: APEX automatically calculates the agar height for each plate based on:
   - Empty plate weight: `r json_data$empty_agar_plate_weight` g
   - Plate weight with agar (specified in the CSV file)
   - Agar density: `r json_data$agar_density` g/cm³

3. **Colony Spotting**: Cells are spotted onto agar plate(s) with the following parameters:
   - Spotting height above agar: `r json_data$spotting_height` mm
   
### Final Plate Layout
Once the protocol is competed, agar plate(s) with spotted cells will have the following layout(s):

```{r destination-plate-image, results='asis', echo=FALSE}
image_files <- list.files(path = params$labware_images_dir, pattern = "\\.png$", full.names = TRUE)
image_files <- sort(image_files)

if(length(image_files) > 0) {
  cat(sprintf('![](%s){width=70\\%%}', image_files[length(image_files)]))
} else {
  cat("*No destination plate image available*")
}
```