---
title: "APEX Instructions"
output: pdf_document
params:
  json_path: NULL
  labware_images_dir: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(rjson)
library(knitr)
json_data <- fromJSON(file = params$json_path)
```
\vspace{-1.5cm}
## Protocol 2: Colony Selection in OT-2

### Overview
Cells are spotted on the total of `r length(json_data$agar_plate_slot) ` agar plates.
The pipette aspirates additional `r json_data$additional_volume` $\mu$L of transformed cells.
The spotting height above the agar is set at `r json_data$spotting_height` (mm).
The agar height is calculated automatically per plate based on:
the plate weight without (`r json_data$empty_agar_plate_weight` g) and with agar (`r json_data$agar_plate_weight` g), 
and agar density of `r json_data$agar_density` ($g cm^{-3}$).

### Preparation
The plates are spotted in `r "$\\mu$L"` according to the layout below.

```{r import-labware-images, results='asis', echo=FALSE}
image_files <- list.files(path = params$labware_images_dir, pattern = "\\.png$", full.names = TRUE)
image_files <- sort(image_files)

for (i in seq_along(image_files)) {
  if (i %% 2 == 1 && i > 1) {
    cat('\\newline\n')
  }
  
  cat(sprintf('![](%s){width=49%%}', image_files[i]))

  if (i %% 2 != 0 && i < length(image_files)) {
    cat(' ')
  }
}
```

### Deck Loading
Check that `r json_data$pipette_name` is in the `r json_data$pipette_mount` mount.  
**Slot `r json_data$tiprack_slots`** load `r json_data$tiprack_name` for the `r json_data$pipette_name` pipette.  
**Slot `r json_data$source_plate_slot`** load `r json_data$source_plate_name` containing cells to be spotted.  
**Slot `r json_data$agar_plate_slot`** load `r json_data$agar_plate_name` with agar.  
