---
title: ""
output: pdf_document
params:
  json_path: NULL
  labware_images_dir: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(rjson)
library(knitr)
json_data <- fromJSON(file = params$json_path)
```

# APEX Instructions
## Protocol 4: Protein Expression Induction in OT-2

### Deck Loading
1. Load pipettes:
   ```{r pipette-check, results='asis'}
   if(is.null(json_data$right_pipette_name) || 
      tolower(json_data$right_pipette_name) == "na" || 
      json_data$right_pipette_name == "NA") {
     cat("   - **Right mount**: No pipette loaded\n")
   } else {
     cat(paste0("   - **Right mount**: Confirm `", json_data$right_pipette_name, "` is properly installed\n"))
   }
   
   # Left pipette check
   if(is.null(json_data$left_pipette_name) || 
      tolower(json_data$left_pipette_name) == "na" || 
      json_data$left_pipette_name == "NA") {
     cat("   - **Left mount**: No pipette loaded\n")
   } else {
     cat(paste0("   - **Left mount**: Confirm `", json_data$left_pipette_name, "` is properly installed\n"))
   }
   ```

2. Load tip racks:
   ```{r tiprack-check, results='asis'}
   # Right pipette tiprack check
   if(!is.null(json_data$right_pipette_name) && 
      tolower(json_data$right_pipette_name) != "na" && 
      json_data$right_pipette_name != "NA") {
     cat(paste0("   - **Slot `", paste(json_data$right_pipette_tiprack_slot, collapse=", "), "`**: Position `", 
               json_data$right_pipette_tiprack_name, "` for use with the `", 
               json_data$right_pipette_name, "` pipette\n"))
   }
   
   # Left pipette tiprack check
   if(!is.null(json_data$left_pipette_name) && 
      tolower(json_data$left_pipette_name) != "na" && 
      json_data$left_pipette_name != "NA") {
     cat(paste0("   - **Slot `", paste(json_data$left_pipette_tiprack_slot, collapse=", "), "`**: Position `", 
               json_data$left_pipette_tiprack_name, "` for use with the `", 
               json_data$left_pipette_name, "` pipette\n"))
   }
   ```

3. Load plates:
   - **Slot `r json_data$culture_plate_slot`**: Place `r json_data$culture_plate_name` containing overnight cultures
   - **Slot `r json_data$media_plate_slot`**: Place `r json_data$media_plate_name` containing fresh antibiotic-media
   - **Slot `r json_data$inducer_plate_slot`**: Place `r json_data$inducer_plate_name` containing chemical inducer
   - **Slot `r json_data$destination_plate_slot`**: Place `r json_data$destination_plate_name` where protein expression will be induced

### Preparation
Prepare reagents and labware according to the plate layout shown below. All volumes are in `r "$\\mu$L"`. Include additional volume for accurate pipetting.

```{r source-plate-images, results='asis', echo=FALSE}
image_files <- list.files(path = params$labware_images_dir, pattern = "\\.png$", full.names = TRUE)
image_files <- sort(image_files)

if(length(image_files) > 1) {
  for (i in 1:(length(image_files)-1)) {
    if (i %% 2 == 1 && i > 1) {
      cat('\n\n')
    }
    cat(sprintf('![](%s){width=49\\%%}', image_files[i]))
    if (i %% 2 != 0 && i < (length(image_files)-1)) {
      cat(' ')
    }
  }
} else {
  cat("*No plate layout images available*")
}
```

### Protocol Execution
1. **Media Distribution**: APEX dispenses fresh antibiotic-containing media into the destination plate.

2. **Culture Inoculation**: APEX resuspends the overnight cultures x times with volume of x and transfers the cells to the destination plate containing fresh media.

3. **Growth Phase**: When prompted by the robot, remove the plate with sub-culture from the deck and incubate it with shaking until cultures reach the desired `r "$OD_{600}$"` value. Return the plate on the deck and resume the protocol.

4. **Induction**: APEX adds chemical inducer to each well to initiate protein expression.

5. **Protein Production**: Continue incubation with shaking for the specified post-induction period to allow protein production.

### Final Plate Layout
Once the protocol is completed, the protein expression plate will have the following layout:

```{r destination-plate-image, results='asis', echo=FALSE}
image_files <- list.files(path = params$labware_images_dir, pattern = "\\.png$", full.names = TRUE)
image_files <- sort(image_files)

if(length(image_files) > 0) {
  cat(sprintf('![](%s){width=70\\%%}', image_files[length(image_files)]))
} else {
  cat("*No destination plate image available*")
}
```