---
title: "APEX Instructions"
output: pdf_document
params:
  json_path: NULL
  labware_images_dir: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(rjson)
library(knitr)
json_data <- fromJSON(file = params$json_path)
```
\vspace{-1.5cm}
## Protocol 4: Protein Expression Induction in OT-2

### Overview
Fresh antibiotic media is distributed into the destination plate, followed by aliquoting and inoculating overnight cultures into this media. 
The cells are then incubated with shaking to reach the desired growth phase. 
After achieving the desired `r "$OD_{600}$"`, a chemical inducer is added to induce protein expression. 
The cultures continue to be incubated with shaking post-induction for protein production.

### Preparation
Prepare the necessary reagents and labware as outlined in the layout provided below. 
Listed volumes are in `r "$\\mu$L"` and indicate the amount of each reagent required. 
Ensure to include an additional volume.

```{r import-labware-images, results='asis', echo=FALSE}
image_files <- list.files(path = params$labware_images_dir, pattern = "\\.png$", full.names = TRUE)
image_files <- sort(image_files)

for (i in seq_along(image_files)) {
  if (i %% 2 == 1 && i > 1) {
    cat('\\newline\n')
  }
  
  cat(sprintf('![](%s){width=49%%}', image_files[i]))

  if (i %% 2 != 0 && i < length(image_files)) {
    cat(' ')
  }
}
```

### Deck Loading
Check that `r json_data$right_pipette_name` is in the right mount and `r json_data$left_pipette_name` is in the left mount.  
**Slot `r json_data$right_pipette_tiprack_slot`** load `r json_data$right_pipette_tiprack_name` for the `r json_data$right_pipette_name` pipette.  
**Slot `r json_data$left_pipette_tiprack_slot`** load `r json_data$left_pipette_tiprack_name` for the `r json_data$left_pipette_name` pipette.  
**Slot `r json_data$media_plate_slot`** load `r json_data$media_plate_name` containing fresh antibiotic-media.  
**Slot `r json_data$inducer_plate_slot`** load `r json_data$inducer_plate_name` containing chemical inducer.  
**Slot `r json_data$culture_plate_slot`** load `r json_data$culture_plate_name` containing overnight cultures.  
**Slot `r json_data$destination_plate_slot`** load `r json_data$inducer_plate_name` where protein expression will be induced.  
