---
title: ""
output: pdf_document
params:
  json_path: NULL
  labware_images_dir: NULL
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(rjson)
library(knitr)
json_data <- fromJSON(file = params$json_path)
```

# APEX Instructions
## Protocol 1: Heat Shock Transformations in OT-2

### Deck Loading
1. Load pipettes:
   ```{r pipette-check, results='asis'}
   if(is.null(json_data$right_pipette_name) || 
      tolower(json_data$right_pipette_name) == "na" || 
      json_data$right_pipette_name == "NA") {
     cat("   - **Right mount**: No pipette loaded\n")
   } else {
     cat(paste0("   - **Right mount**: Confirm `", json_data$right_pipette_name, "` is properly installed\n"))
   }
   if(is.null(json_data$left_pipette_name) || 
      tolower(json_data$left_pipette_name) == "na" || 
      json_data$left_pipette_name == "NA") {
     cat("   - **Left mount**: No pipette loaded\n")
   } else {
     cat(paste0("   - **Left mount**: Confirm `", json_data$left_pipette_name, "` is properly installed\n"))
   }
   ```

2. Load tip racks:
   ```{r tiprack-check, results='asis'}
   if(!is.null(json_data$right_pipette_name) && 
      tolower(json_data$right_pipette_name) != "na" && 
      json_data$right_pipette_name != "NA") {
     cat(paste0("   - **Slot `", paste(json_data$right_pipette_tiprack_slot, collapse=", "), "`**: Place `", 
               json_data$right_pipette_tiprack_name, "` for use with the `", 
               json_data$right_pipette_name, "` pipette\n"))
   }
   if(!is.null(json_data$left_pipette_name) && 
      tolower(json_data$left_pipette_name) != "na" && 
      json_data$left_pipette_name != "NA") {
     cat(paste0("   - **Slot `", paste(json_data$left_pipette_tiprack_slot, collapse=", "), "`**: Place `", 
               json_data$left_pipette_tiprack_name, "` for use with the `", 
               json_data$left_pipette_name, "` pipette\n"))
   }
   ```
3. Load plates and modules:
   - **Slot `r json_data$dna_plate_slot`**: Place `r json_data$dna_plate_name` containing DNA
   - **Slot `r json_data$cells_plate_slot`**: Place `r json_data$cells_plate_name` containing competent cells
   - **Slot `r json_data$media_plate_slot`**: Place `r json_data$media_plate_name` containing recovery medium
   - **Slots 7, 8, 10, 11**: Load a thermocycler module and power it on. You will be prompted to load `r json_data$transformation_plate_name` into the thermocycler during the protocol.

### Preparation
Prepare reagents and labware according to the plate layout shown below. All volumes are in `r "$\\mu$L"`. Include additional volume for accurate pipetting.

```{r source-plate-images, results='asis', echo=FALSE}
image_files <- list.files(path = params$labware_images_dir, pattern = "\\.png$", full.names = TRUE)
image_files <- sort(image_files)

if(length(image_files) > 1) {
  for (i in 1:(length(image_files)-1)) {
    if (i %% 2 == 1 && i > 1) {
      cat('\n\n')
    }
    cat(sprintf('![](%s){width=49\\%%}', image_files[i]))
    if (i %% 2 != 0 && i < (length(image_files)-1)) {
      cat(' ')
    }
  }
} else {
  cat("*No plate layout images available*")
}
```

### Protocol Execution
1. **Competent Cell Distribution**: APEX distributes competent cells into the transformation plate in the thermocycler.

2. **DNA Addition**: APEX transfers DNA samples to the wells containing competent cells.

3. **Pre-Heat Shock Incubation**: 
   - Temperature: `r json_data$pre_shock_incubation_temp` °C 
   - Duration: `r json_data$pre_shock_incubation_time` minutes

4. **Heat Shock**: 
   - Temperature: `r json_data$heat_shock_temp` °C 
   - Duration: `r json_data$heat_shock_time` seconds

5. **Post-Heat Shock Incubation**: 
   - Temperature: `r json_data$post_shock_incubation_temp` °C 
   - Duration: `r json_data$post_shock_incubation_time` minutes

6. **Recovery**: 
   - APEX transfers recovery medium to the transformed cells
   - Temperature: `r json_data$recovery_temp` °C 
   - Duration: `r json_data$recovery_time` minutes

### Final Plate Layout
Once the protocol is completed, the transformation plate will have the following layout:

```{r destination-plate-image, results='asis', echo=FALSE}
image_files <- list.files(path = params$labware_images_dir, pattern = "\\.png$", full.names = TRUE)
image_files <- sort(image_files)

if(length(image_files) > 0) {
  cat(sprintf('![](%s){width=70\\%%}', image_files[length(image_files)]))
} else {
  cat("*No destination plate image available*")
}
```