---
title: ""
output: pdf_document
params:
  json_path: NULL
  labware_images_dir: NULL
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(rjson)
library(knitr)
json_data <- fromJSON(file = params$json_path)
```

# APEX Instructions
## Protocol 3: Colony Sampling in OT-2

### Deck Loading
1. Load pipettes:
   ```{r pipette-check, results='asis'}
   if(is.null(json_data$right_pipette_name) || 
      tolower(json_data$right_pipette_name) == "na" || 
      json_data$right_pipette_name == "NA") {
     cat("   - **Right mount**: No pipette loaded\n")
   } else {
     cat(paste0("   - **Right mount**: Confirm `", json_data$right_pipette_name, "` is properly installed\n"))
   }
   if(is.null(json_data$left_pipette_name) || 
      tolower(json_data$left_pipette_name) == "na" || 
      json_data$left_pipette_name == "NA") {
     cat("   - **Left mount**: No pipette loaded\n")
   } else {
     cat(paste0("   - **Left mount**: Confirm `", json_data$left_pipette_name, "` is properly installed\n"))
   }
   ```

2. Load tip racks:
   ```{r tiprack-check, results='asis'}
   if(!is.null(json_data$right_pipette_name) && 
      tolower(json_data$right_pipette_name) != "na" && 
      json_data$right_pipette_name != "NA") {
     cat(paste0("   - **Slot `", paste(json_data$right_pipette_tiprack_slot, collapse=", "), "`**: Place `", 
               json_data$right_pipette_tiprack_name, "` for use with the `", 
               json_data$right_pipette_name, "` pipette\n"))
   }
   if(!is.null(json_data$left_pipette_name) && 
      tolower(json_data$left_pipette_name) != "na" && 
      json_data$left_pipette_name != "NA") {
     cat(paste0("   - **Slot `", paste(json_data$left_pipette_tiprack_slot, collapse=", "), "`**: Place `", 
               json_data$left_pipette_tiprack_name, "` for use with the `", 
               json_data$left_pipette_name, "` pipette\n"))
   }
   ```

3. Load plates:
   - **Slot `r json_data$media_plate_slot`**: Place `r json_data$media_plate_name` containing fresh media with antibiotic
   - **Slot `r json_data$agar_plate_slot`**: Place `r json_data$agar_plate_name` containing agar with developed colonies
   - **Slot `r json_data$destination_plate_slot`**: Place `r json_data$destination_plate_name` where fresh media will be distributed and sampled cells propagated

### Preparation
Prepare reagents and labware according to the plate layout shown below. All volumes are in `r "$\\mu$L"`. Include additional volume for accurate pipetting.

```{r source-plate-images, results='asis', echo=FALSE}
image_files <- list.files(path = params$labware_images_dir, pattern = "\\.png$", full.names = TRUE)
image_files <- sort(image_files)

if(length(image_files) > 1) {
  for (i in 1:(length(image_files)-1)) {
    if (i %% 2 == 1 && i > 1) {
      cat('\n\n')
    }
    
    cat(sprintf('![](%s){width=49\\%%}', image_files[i]))

    if (i %% 2 != 0 && i < (length(image_files)-1)) {
      cat(' ')
    }
  }
} else {
  cat("*No plate layout images available*")
}
```

### Protocol Execution
1. **Media Distribution**: APEX dispenses fresh media containing antibiotic into the destination plate.

2. **Colony Sampling**: APEX uses pipette tips to sample colonies from the agar plates with the following parameters:
```{r sampling-params, results='asis'}
   cat(paste0("   - Picking depth into agar: ", json_data$agar_pierce_depth, " mm\n"))
   cat(paste0("   - Sampling method: ", json_data$sampling_method, "\n"))
   if(!is.null(json_data$sampling_method) && 
      tolower(json_data$sampling_method) == "spiral") {
     cat(paste0("   - Spot radius: ", json_data$spot_radius, " mm\n"))
     cat(paste0("   - Number of spiral points: ", json_data$spiral_points, "\n"))
     cat(paste0("   - Number of spiral rotations: ", json_data$spiral_rotations, "\n"))
   }
```
   
3. **Agar Height Calculation**: The system automatically calculates the agar height for each plate based on:
   - Empty plate weight: `r json_data$empty_agar_plate_weight` g
   - Plate weight with agar: `r json_data$agar_plate_weight` g
   - Agar density: `r json_data$agar_density` g/cm³

4. **Cell Transfer**: Sampled colonies are transferred to the destination plate containing fresh media for propagation.

### Final Plate Layout
Once the protocol is completed, the culture plate will have the following layout:

```{r destination-plate-image, results='asis', echo=FALSE}
image_files <- list.files(path = params$labware_images_dir, pattern = "\\.png$", full.names = TRUE)
image_files <- sort(image_files)
if(length(image_files) > 0) {
  cat(sprintf('![](%s){width=70\\%%}', image_files[length(image_files)]))
} else {
  cat("*No destination plate image available*")
}
```