---
title: "APEX Instructions"
output: pdf_document
params:
  json_path: NULL
  labware_images_dir: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(rjson)
library(knitr)
json_data <- fromJSON(file = params$json_path)
```
\vspace{-1.5cm}
## Protocol 3: Colony Sampling in OT-2

### Overview
Media with supplemented antibtiotic is distributed into the destination plate.
The colonies are sampled using a pipette tip and transferred to destination plate.
Colonies are sampled from total of `r length(json_data$agar_plate_slot) ` agar plates.
The picking height into the agar is set at `r json_data$agar_pierce_depth` (mm).
The agar height is calculated automatically per plate based on:
the plate weight without (`r json_data$empty_agar_plate_weight` g) and with agar (`r json_data$agar_plate_weight` g), 
and agar density of `r json_data$agar_density` ($g cm^{-3}$).

### Preparation
The colonies are sampled according to the plate layout below.

```{r import-labware-images, results='asis', echo=FALSE}
image_files <- list.files(path = params$labware_images_dir, pattern = "\\.png$", full.names = TRUE)
image_files <- sort(image_files)

for (i in seq_along(image_files)) {
  if (i %% 2 == 1 && i > 1) {
    cat('\\newline\n')
  }
  
  cat(sprintf('![](%s){width=49%%}', image_files[i]))

  if (i %% 2 != 0 && i < length(image_files)) {
    cat(' ')
  }
}
```

### Deck Loading
Check that `r json_data$right_pipette_name` is in the right mount and `r json_data$left_pipette_name` is in the left mount.  
**Slot `r json_data$right_pipette_tiprack_slot`** load `r json_data$right_pipette_tiprack_name` for the `r json_data$right_pipette_name` pipette.  
**Slot `r json_data$left_pipette_tiprack_slot`** load `r json_data$left_pipette_tiprack_name` for the `r json_data$left_pipette_name` pipette.  
**Slot `r json_data$media_plate_slot`** load `r json_data$media_plate_name` containing fresh media with antibiotic.  
**Slot `r json_data$agar_plate_slot`** load `r json_data$agar_plate_name` containing agar with developed colonies.  
**Slot `r json_data$destination_plate_slot`** load `r json_data$destination_plate_name` where fresh media will be distributed and sampled cells propagated.  
